### 2016-12-12 README.Rmd
updated revdep check, update new and cran comments, bump to v0.8

taxize
=======

@@

The `taxize` tutorial is can be found at [https://ropensci.org/tutorials/taxize.html][tut].

@@

Note that a few data sources require SOAP web services, which are difficult to support in R across all operating systems. These include: World Register of Marine Species, Pan-European Species directories Infrastructure , and Mycobank, so far. Data sources that use SOAP web services have been moved to a new package called `taxizesoap`. Find it at [https://github.com/ropensci/taxizesoap](https://github.com/ropensci/taxizesoap).

@@

@@

Windows users install [Rtools](http://cran.r-project.org/bin/windows/Rtools/) first.

@@

+ [Scott Chamberlain](https://github.com/sckott)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Karthik Ram](https://github.com/karthik)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
+ [James O'Donnell](https://github.com/jimmyodonnell)
+ [Francois Michonneau](https://github.com/fmichonneau)
+ [Philippe Marchand](https://github.com/pmarchand1)
+ [Jari Oksanen](https://github.com/jarioksa)
+ [Oliver Keyes](https://github.com/Ironholds)
+ [Luis Villanueva](https://github.com/ljvillanueva)
+ [David LeBauer](https://github.com/dlebauer)
+ [Ben Marwick](https://github.com/benmarwick)

@@

[![ropensci](http://ropensci.org/public_images/github_footer.png)](http://ropensci.org)

[tut]: http://ropensci.org/tutorials/taxize.html

>>>>

taxize
======

@@

The `taxize` tutorial is can be found at <https://ropensci.org/tutorials/taxize.html>

@@

Note that a few data sources require SOAP web services, which are difficult to support in R across all operating systems. These include: World Register of Marine Species, Pan-European Species directories Infrastructure , and Mycobank, so far. Data sources that use SOAP web services have been moved to a new package called `taxizesoap`. Find it at <https://github.com/ropensci/taxizesoap>.

@@

	<td style="text-align:left;">Open Tree of Life (TOL)</td>
	<td style="text-align:left;"><code>tol</code></td>
	<td style="text-align:left;"><a href="https://opentreeoflife.org">link</a></td>

@@

Windows users install [Rtools](https://cran.r-project.org/bin/windows/Rtools/) first.

@@

Alphebetical

+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Joseph Brown](https://github.com/josephwb)
+ [Scott Chamberlain](https://github.com/sckott)
+ [Anirvan Chatterjee](https://github.com/anirvan)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Oliver Keyes](https://github.com/Ironholds)
+ [David LeBauer](https://github.com/dlebauer)
+ [Philippe Marchand](https://github.com/pmarchand1)
+ [Ben Marwick](https://github.com/benmarwick)
+ [Francois Michonneau](https://github.com/fmichonneau)
+ [James O'Donnell](https://github.com/jimmyodonnell)
+ [Jari Oksanen](https://github.com/jarioksa)
+ [Karthik Ram](https://github.com/karthik)
+ [raredd](https://github.com/raredd)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Luis Villanueva](https://github.com/ljvillanueva)
+ [Jakub Wilk](https://github.com/jwilk)

@@

[![ropensci](https://ropensci.org/public_images/github_footer.png)](https://ropensci.org)

[tut]: https://ropensci.org/tutorials/taxize.html
